Usage metrics

### 2020-12-15 analysis/usage.Rmd
Fix cases when one of the variant is absent from the dataset.

trig_eval <- sites_per_variant %>% filter(ev_variant == "eval") %>% .$n
trig_evalq <- sites_per_variant %>% filter(ev_variant == "evalq") %>% .$n
trig_eval.parent <- sites_per_variant %>% filter(ev_variant == "eval.parent") %>% .$n
trig_local <- sites_per_variant %>% filter(ev_variant == "local") %>% .$n

>>>>

trig_eval <- sites_per_variant %>% filter(ev_variant == "eval")
trig_eval <- if(nrow(trig_eval) == 0)
{
  0
} else
{
  trig_eval$n
}

trig_evalq <- sites_per_variant %>% filter(ev_variant == "evalq")
trig_evalq <- if(nrow(trig_evalq) == 0)
{
  0
} else
{
  trig_evalq$n
}
trig_eval.parent <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
trig_eval.parent <- if(nrow(trig_eval.parent) == 0)
{
  0
} else
{
  trig_eval.parent$n
}
trig_local <- sites_per_variant %>% filter(ev_variant == "local") %>% .$n
trig_local <- if(nrow(trig_local) == 0)
{
  0
} else
{
  trig_local$n
}
